Optimal (Multiway) Spatial Joins

### 2024-05-24 msj.tex
yufei

        \item Consider any $k$-tuple $\bm{t} \in \J(R'_1, ..., R'_{k-2})$. Let $r' = \gbot(\bm{t})$ and $r^*$ be the top-sliced rectangle of $r'$. Then, it must hold that $\dcross_H(\bm{t}) \subseteq \cross_H(r^*)$. Furthermore, if the segments of $\cross_H(r^*)$ have been sorted in ascending order, then $\dcross_H(\bm{t})$ includes a prefix of the sorted order.
    }
\end{lemma}

Finding the $\cross_H(r^*)$ sets of all $r^* \in R^*_i$ is an instance of the find-all-sorted version of Problem $\mathscr{D}$. Statement (1) of the above lemma assures us that

>>>>

        \item Consider any $k$-tuple $\bm{t} \in \J(R'_1, ..., R'_{k-2})$. Let $r' = \gbot(\bm{t})$ and $r^*$ be the top-sliced rectangle of $r'$. Then, it must hold that $\dcross_H(\bm{t}) \subseteq \cross_H(r^*)$. Furthermore, if the (horizontal) segments of $\cross_H(r^*)$ have been sorted in ascending order of y-coordinate, then $\dcross_H(\bm{t})$ includes a prefix of the sorted order.
    }
\end{lemma}

Finding the $\cross_H(r^*)$ sets of all $r^* \in R^*_i$ is an instance of the find-all-sorted version of Problem $\mathscr{D}$. Statement (1) of the above lemma assures us that the total time to do so for all $R^*_1, ..., R^*_{k-2}$ is $O(n \log n + \out)$. Note that, for each $\cross_H(r^*)$ computed, the (horizontal) segments therein has been sorted in ascending order of y-coordinate.
